SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-05 scipy-1.0/paper.tex
Add NumPy -> SciPy -> scikits description
Weave probably happened mostly as part of Enthought

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  It is the foundation upon which higher level scientific
libraries, including scikit-learn and scikit-image, are built.

@@

% PhD Mayo Clinic, started faculty position at BYU in 2001
By the late 1990s, discussions appeared on Matrix-SIG,
expressing a desire for a complete scientific data analysis environment\footnote{https://conference.scipy.org/scipy2010/slides/travis\_oliphant\_keynote.pdf}.
Travis Oliphant, a PhD student at the Mayo Clinic,
released a number of packages\footnote{https://web.archive.org/web/19990125091242/http://oliphant.netpedia.net:80/}\footnote{https://web.archive.org/web/20001206213500/http://oliphant.netpedia.net:80/} that built on top of the Numeric array
package, and provided algorithms for signal processing, special
functions, sparse matrices, quadrature, optimization, and Fast Fourier
Transforms, and more.  One of these packages, Multipack, was a set of
extension modules that wrapped Fortran and C libraries such as
ODEPACK, QUADPACK, and MINPACK, to solve and minimize nonlinear
equations, integrate differential equations, and fit splines (the
latter implemented by Pearu Peterson).  Robert Kern, then an
undergraduate student (and currently a SciPy core developer), provided
compilation instructions under Windows.
% 2001 PhD Tallinn Technical University
Around the same time, Pearu Peterson, a PhD student from Estonia,
released f2py\footnote{https://mail.python.org/pipermail/numpy-discussion/2000-September/000243.html}, a command line tool for binding Python and Fortran
codes, and wrote modules for linear algebra and interpolation.
% Graduated 1999, Duke
Eric Jones, while a graduate student at Duke, wrote a number of
packages to support his dissertation, including a parallel job
scheduler, genetic optimizer, and inline C++ compiler.
% Graduated 1998, PhD from Brown, 97–99 postdoc at Harvard Medical
% School; at Harvard ever since
%
% https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
Gary Strangman, a postdoctoral fellow at Harvard Medical School,
published several descriptive and inferential statistical routines\footnote{https://web.archive.org/web/20001022231108/http://www.nmr.mgh.harvard.edu/Neural\_Systems\_Group/gary/python.html}.

>>>>

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn
and scikit-image, are built.

@@

% PhD Mayo Clinic, started faculty position at BYU in 2001
By the late 1990s, discussions appeared on Matrix-SIG,
expressing a desire for a complete scientific data analysis environment\footnote{https://conference.scipy.org/scipy2010/slides/travis\_oliphant\_keynote.pdf}.
Travis Oliphant, a PhD student at the Mayo Clinic,
released a number of packages\footnote{https://web.archive.org/web/19990125091242/http://oliphant.netpedia.net:80/}\footnote{https://web.archive.org/web/20001206213500/http://oliphant.netpedia.net:80/} that built on top of the Numeric array
package, and provided algorithms for signal processing, special
functions, sparse matrices, quadrature, optimization, and Fast Fourier
Transforms, and more.  One of these packages, Multipack, was a set of
extension modules that wrapped Fortran and C libraries such as
ODEPACK, QUADPACK, and MINPACK, to solve and minimize nonlinear
equations, integrate differential equations, and fit splines (the
latter implemented by Pearu Peterson).  Robert Kern, then an
undergraduate student (and currently a SciPy core developer), provided
compilation instructions under Windows.
% 2001 PhD Tallinn Technical University
Around the same time, Pearu Peterson, a PhD student from Estonia,
released f2py\footnote{https://mail.python.org/pipermail/numpy-discussion/2000-September/000243.html}, a command line tool for binding Python and Fortran
codes, and wrote modules for linear algebra and interpolation.
% Graduated 1999, Duke
Eric Jones, while a graduate student at Duke, wrote a number of
packages to support his dissertation, including a parallel job
scheduler and genetic optimizer.
% Graduated 1998, PhD from Brown, 97–99 postdoc at Harvard Medical
% School; at Harvard ever since
%
% https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
Gary Strangman, a postdoctoral fellow at Harvard Medical School,
published several descriptive and inferential statistical routines\footnote{https://web.archive.org/web/20001022231108/http://www.nmr.mgh.harvard.edu/Neural\_Systems\_Group/gary/python.html}.
